---
title: "Data analysis"
author: "Florian Leprevost"
date: "21/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(root.dir = 'SART_PCBS')

```

# Objectives
List of data wrangling and analysis to do:

- [ ] Putting it in dataframes
  - [ ] Read .xpd files with R
  - [ ] Change .txt files into .csv before reading them
  
- [ ] Augment the dataframe with:
  - [ ] probes results (need to be converted from key value to numbers --> 1-9 = 49-57)
  - [ ] reaction time variability in the last 8 trials (see [Bastian & Sackur 2013](https://www.frontiersin.org/articles/10.3389/fpsyg.2013.00573/full) )
  - [ ] mean reaction time in the 8 preceding trials
  
- Try and reproduce Seli's results
  - [ ] calculate mindwandering rate by type
    - 
  - [ ] bin categories to match their data 
    - deliberate or spontaneous mind wandering = controlled (6-9) or uncontrolled (1-4) unrelated thoughts (1-4)
  - [ ] mixed ANOVA (with difficulty as between subject, mind-wandering type as within subject, and rate as dependent variable) 
  
- Other tests
  - [ ] Regression of reaction time variability by control * relatedness
  - [ ] PCA? 
  - [ ] MVPA?
  

#Dataframe
Need the tidyverse

```{r}
library(tidyverse)
```
read xpd with function from documentation
```{r echo=false}
setwd('C:/Users/install/SART_PCBS')
source('expyriment_data.R')
```

```{r}
dtf= read.expyriment.data("data", "SART_task_easy")
```


change txt files (probe data) in csv before transforming them in dataframes

```{r}
files <- list.files(pattern="*.txt")
newfiles <- gsub(".txt$", ".csv", files)
file.rename(files, newfiles)
```



