---
title: "Data analysis"
author: "Florian Leprevost"
date: "21/11/2019"
output:
  prettydoc::html_pretty:
    theme: leonids
    highlight: github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Objectives
List of data wrangling and analysis to do:

- [x] Putting it in dataframes
  - [x] Read .xpd files with R
  - [x] Change .txt files into .csv before reading them
  - [x] Add subject id and difficulty
  
- [x] Augment the dataframe with:
  - [x] probes results (need to be converted from key value to numbers --> 1-9 = 49-57)
  - [x] reaction time variability in the last 8 trials (see [Bastian & Sackur 2013](https://www.frontiersin.org/articles/10.3389/fpsyg.2013.00573/full) )
  - [x] mean reaction time in the 8 preceding trials
  
- Try and reproduce Seli's results
  - [x] calculate mindwandering rate by type *(finally I only plotted it)*
    - (number of deliberate mindwandering reports on total number of reports reports)
  - [x] bin categories to match their data 
    - deliberate or spontaneous mind wandering = controlled (6-9) or uncontrolled (1-4) unrelated thoughts (1-4)
  - [ ] mixed ANOVA (with difficulty as between subject, mind-wandering type as within subject, and rate as dependent variable) 
  
- Other tests
  - [ ] Regression of reaction time variability by control * relatedness
  - [ ] PCA? 
  - [ ] MVPA?
  

# 2. Dataframe 
Need the tidyverse

```{r message=F, warning=F}
library(tidyverse)
```
## 2.1 SART files (.xpd)

Read xpd with function from documentation
```{r}
#setwd('C:/Users/install/SART_PCBS')
source('expyriment_data.R')
```
Read and add difficulty
```{r message=F, warning=F}
dtf_sart_easy= read.expyriment.data("data", "SART_task_easy")
dtf_sart_normal= read.expyriment.data("data", "SART_task_0")

#add difficulty
dtf_sart_easy <- dtf_sart_easy %>% 
  mutate(difficulty=0)
dtf_sart_normal <- dtf_sart_normal %>% 
  mutate(difficulty=1)
```
Join
```{r}
dtf_sart = bind_rows(dtf_sart_easy, dtf_sart_normal)
glimpse(dtf_sart)
```



## 2.2 Probes files (.txt)


Change txt files (probe data) in csv before transforming them in dataframes

```{r message=F, warning=F}
files <- list.files(pattern="*.txt")
newfiles <- gsub(".txt$", ".csv", files)
file.rename(files, newfiles)
```

```{r}
#get file names
files= list.files(pattern=".csv$")
files_easy = grep("^probe_data_easy", files, value=T)
files_normal = grep("^probe_data_easy", files, value=T, invert=T)
```

Tried the following complicated method but it didn't work
```{r eval=FALSE}
#get the difficulty indice and the subject id
difficulty=list()
subject_id=list()

for (el in files) {
  if (substr(el, 12,15) == "easy")  {
    difficulty[length(difficulty)+1]=0
    subject_id[length(subject_id)+1]=substr(el, 16,16)

  }else{
    difficulty[length(difficulty)+1]=1
    subject_id[length(subject_id)+1]=substr(el, 11,11)
  }
}

#read files
several_dtf = lapply(files, read.csv)
#add missing parameters to dataframes
for (ind in length(several_dtf)){
  several_dtf[ind] <- several_dtf[ind] %>%
    mutate("subject_id"=pull(subject_id[ind])) %>%
    mutate("difficulty"=pull(difficulty[ind]))
}
#bind dataframes
dtf_probes = do.call(rbind, several_dtf)

```
So i cheated a little, using the fact that the subject's files are in order. I indeed used the .id parameter to re-generate subject_id. Then I used mutate to add difficulty
```{r message=F, warning=F}
#add subject-id
several_dtf_easy = lapply(files_easy, read.csv)
dtf_probes_easy= bind_rows(several_dtf_easy, .id= "subject_id")

several_dtf_normal = lapply(files_normal, read.csv)
dtf_probes_normal= bind_rows(several_dtf_normal, .id= "subject_id")

#add difficulty
dtf_probes_easy <- dtf_probes_easy %>% 
  mutate(difficulty=0)
dtf_probes_normal <- dtf_probes_normal %>% 
  mutate(difficulty=1)

#join
dtf_probes = bind_rows(dtf_probes_easy, dtf_probes_normal)

#preview
glimpse(dtf_probes)
```

Simple method to transform the keys into numbers
```{r}
#create some kind of dictionnary
dico= 1:9
names(dico)=49:57
#transform into numbers
dtf_probes <- dtf_probes %>% 
  mutate(relatedness= dico[as.character(relatedness)]) %>% 
  mutate(control=dico[as.character(control)])

glimpse(dtf_probes)
```


## 2.3 Get rtv in dtf probes
```{r}
indices = -8:-1

list_mean=list()
list_rtv=list()

for (probe in 1:nrow(dtf_probes))
{
  #I realised I didn't control the first probe is not after 8 trials
  if (dtf_probes$trial_number[probe] >= 8)
  {
    data_interest <- dtf_sart %>% 
      filter(subject_id==dtf_probes$subject_id[probe],
             block_name==dtf_probes$block_number[probe], 
             difficulty ==dtf_probes$difficulty[probe])
    
    eight_trials=dtf_probes$trial_number[probe] + indices
    mean_rt = mean(data_interest$rt[eight_trials], na.rm=T)
    rtv= sd(data_interest$rt[eight_trials], na.rm=T)
  }
  else {
    mean_rt=as.numeric(NA)
    rtv=as.numeric(NA)
  }
  list_mean = c(list_mean, mean_rt)
  list_rtv = c(list_rtv,rtv)
}

#add it in dataframe
dtf_probes$mean_RT = unlist(list_mean)
dtf_probes$RTV = unlist(list_rtv)

```
# 3.EDA
## EDA Plots
```{r warning=F}
attach(dtf_probes)
par(mfrow=c(2,2))
hist(control)
hist(relatedness)
hist(RTV)
hist(mean_RT)
detach(dtf_probes)


ggplot(dtf_probes, aes(x=relatedness, y=control, size=RTV, color= as.factor(difficulty)))+
  geom_point()

ggplot(dtf_probes, aes(x=relatedness, y=mean_RT))+
  geom_point()+
  facet_wrap(~ difficulty)

ggplot(dtf_probes, aes(x=control, y=mean_RT))+
  geom_point()+
  facet_wrap(~ difficulty)

ggplot(dtf_probes, aes(x=relatedness, y=RTV))+
  geom_point()+
  facet_wrap(~ difficulty)

ggplot(dtf_probes, aes(x=control, y=RTV))+
  geom_point()+
  facet_wrap(~ difficulty)



```

The plots seem to indicate several things
- control and relatedness seem independent
- RTV seem predicted by relatedness (especially in the normal difficulty condition)
- RTV seem larger in the easy difficulty condition
- 

# 3.2 Basics stats
We can follow with some statistical tests (I know the data is not normal, but I don't really know about the alternative, so this is just some ideas)
```{r}
#independence of control and relatedness
chisq.test(dtf_probes$control, dtf_probes$relatedness)
```
Control & relatedness are significantly independent.

Linear regressions
```{r}
summary(lm(RTV~ control+relatedness+difficulty, dtf_probes))
```
Only **difficulty** is a significant predictor of RTV.

```{r}
summary(lm(mean_RT~ control+relatedness+difficulty, dtf_probes))
```
Nothing
```{r}
summary(lm(RTV~ control*difficulty, dtf_probes))

```
But with only difficulty and control (and their interaction effect), control is almost a significant predictor of RTV.

## 3.3 Reproduce Seli's

Reshape data to match
```{r}

data_seli <- dtf_probes %>% 
  mutate(intention=ifelse(control>4, "deliberate", "spontaneous")) %>% 
  mutate(on_off= ifelse(relatedness<6, "off", "on"))
```

```{r}
#switch on_off order

data_seli$on_off <- factor(data_seli$on_off, levels = c("on", "off"))

#plot
ggplot(data_seli, aes(x=as.factor(difficulty), fill=as.factor(on_off)))+
  geom_bar()+
  facet_grid(~ intention)
```


Not really reproduced: both deliberate and spontaneous mindwandering increase with difficulty

# 4. Conclusion
I would have like to try more analysis, but I lack time, and it wouldn't be much interesting with as little data anyway. I still feel I learned a lot by doing such a big project, from the conception of the experiment to automatizing the data analysis.